%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-10pt} % Adjust the value as needed
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-1pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Priyabrata Mondal} \\
    \vspace{1pt}
    \small +91 6297559892 $|$ \href{mailto:priyabrata8558@gmail.com}{\textbf{priyabrata8558@gmail.com}} $|$ 
    \href{https://priyabratamondal.com}{\textbf{Portfolio}} $|$ 
    \href{https://github.com/PriyabrataMo}{\textbf{Github}} $|$ 
    \href{https://www.linkedin.com/in/priyabrata-mondal/}{\textbf{LinkedIn}} $|$
    \href{https://leetcode.com/prybruhta/}{\textbf{LeetCode}} $|$
    \href{https://codeforces.com/profile/priyabrata8558}{\textbf{Codeforces}} \\
    Kolkata, West Bengal, India
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Techno Main Salt Lake}{Kolkata, West Bengal, India}
      {Bachelor of Technology in Computer Science and Business Systems; CGPA: 8.55}{Oct. 2021 -- May 2025}
    \resumeSubheading
      {Guru Tegh Bahadur Public School}{Durgapur, West Bengal, India}
      {Senior Secondary (XII); Percentage: 90.8\%}{2020 - 2021}
    \resumeSubheading
      {Guru Tegh Bahadur Public School}{Durgapur, West Bengal, India}
      {Higher Secondary (X); Percentage: 93.6\%}{2018 - 2019}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
    \resumeItemListStart
        \resumeItem{\textbf{Programming Languages}: C, C++, Python, JavaScript, Typescript, Go}
        \resumeItem{\textbf{Databases}: MySQL, SQLPlus, MongoDB}
        \resumeItem{\textbf{Frameworks}: NLTK, Scikit-learn, Pandas, Numpy, Express.js, Node.js, Next.js, Rest APIs}
        \resumeItem{\textbf{Developer Tools}: Git, VS Code, Postman, Docker, AWS, GCP}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Experience / Open-Source}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{SCALE AI (Outlier) - C++ AI Trainer (Freelance)}}{Oct 2024}
    \resumeItemListStart
        \resumeItem{Conducted A/B testing on 50+ AI model responses, optimizing performance using C++.}
        \resumeItem{Created 10+ complex prompts to improve model training and achieve higher accuracy.}
        \resumeItem{Evaluated over 200 AI responses for accuracy, relevance, and quality across predefined categories.}
        \resumeItem{Provided targeted feedback that led to improvement in AI decision-making and output quality.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Pyccel}}{Jan 2024}
    \resumeItemListStart
        \resumeItem{Added support for \texttt{numpy.max} and \texttt{numpy.min} in the C printer, including macro definitions, AST updates, and Fortran support for complex numbers.}
        \resumeItem{Resolved issue \#1645 by replacing deprecated AST classes with \texttt{Constant} (Python 3.8+), ensuring compatibility with newer Python versions.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Personal Portfolio}}{\href{https://priyabratamondal.com}{Link}}
    \resumeItemListStart
        \resumeItem{Developed a responsive portfolio website using Next.js, TypeScript, and Tailwind CSS to showcase projects and skills.}
        \resumeItem{Designed a clean and modern UI with optimized performance and SEO best practices.}
        \resumeItem{Deployed the website on Vercel for seamless hosting and continuous deployment.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeProjectHeading
            {\textbf{Predicting Stack Overflow Tags}}{\href{https://github.com/PriyabrataMo/predicting-stackoverflow-tags}{Github Link}}
            \resumeItemListStart
                \resumeItem{Trained a machine learning model to autonomously tag Stack Overflow posts, eliminating the need for manual tagging.}
                \resumeItem{Utilized natural language processing (NLP) techniques to analyze and process the content of the posts.}
                \resumeItem{Achieved an F1 score of 0.61, indicating the model's accuracy and effectiveness in predicting tags.}
                \resumeItem{Created an API using FastAPI to deploy the machine learning model, enabling seamless integration and usage in various applications.}
            \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------HONORS & AWARDS-----------
\section{Honors \& Awards}
\resumeSubHeadingListStart
\resumeItem{Achieved a \texttt{2123 rating} (\texttt{Knight}) and ranked in the top 1.5\% of Leetcode users.}
\resumeItem{Solved 2000+ DSA problems across all platforms.}  
\resumeItem{Selected for \texttt{Amazon Machine Learning Summer School 2024}.}  
\resumeItem{Qualified for Round 2 in the \texttt{Meta Hacker Cup 2024}.}  

\resumeSubHeadingListEnd

\end{document}

